Basic simulations with EpiCompare

### 2020-11-05 jss/jss-article-rnw/chapters/ch1-intro-v2.Rnw

As the availability of scientific resources has increased through the decades, the number of models to analyze a particular disease outbreak has also increased.  This phenomenon is evidenced by the appearance of dozens of publicly available estimates of the reproduction number $R_0$ for COVID-19 \citep[e.g.][]{Sanche2020a}, and is well documented in many literature reviews in epidemology \citep[e.g.][]{Canzani2015}.  As both the quantity of data and models increase, so does the need for standard and fair comparisons of models, as according to the data analysis pipeline of infectious diseases.\footnote{\ben{Is our tool more a "after the fact" analysis than some works?}}

@@

The goal of \pkg{EpiCompare} is not to supplant existing infectious disease modeling tools and software but, rather, is a concerted effort to create standard and fair comparisons among models developed for disease outbreaks and outbreak data. \pkg{EpiCompare}'s major unique contribution to the existing approaches is a set of time-invariant tools (motivated in more detail in Section \ref{sec:time-invariant}).More broadly, \pkg{EpiCompare} aids the data analysis pipeline for infecetious diseases by
\begin{enumerate}
  \item Standardizing outputs from common \proglang{R}-based infectious disease model software and common data storage types
  \item Expanding upon existing data visualization and EDA tools (especially in 3 state models like SIR models).
  \item Providing a interface for simple ODE-style agent based modeling.
  \item Aiding in comparison and assessment of models through time invariant analysis and conformal prediction bands and comparisons.
\end{enumerate}
Although \pkg{EpiCompare} aids in every part of the pipeline, our tools especially emphasize improvements for pipeline parts (1) and (4) which can be summarized as data input and output harmonization and contributions to fairly comparing models and data to one another.

>>>>

The availability of scientific resources has increased through the decades, the number of models to analyze a particular disease outbreak has also increased.  This phenomenon is evidenced by the appearance of dozens of publicly available estimates of the reproduction number $R_0$ for COVID-19 \citep[e.g.][]{Sanche2020a}, and is well documented in many literature reviews in epidemology \citep[e.g.][]{Canzani2015}.  As both the quantity of data and models increase, so does the need for standard and fair comparisons of models, as according to the data analysis pipeline of infectious diseases.\footnote{\ben{Is our tool more a "after the fact" analysis than some works?}}

@@

The goal of \pkg{EpiCompare} is not to supplant existing infectious disease modeling tools and software but, rather, is a concerted effort to create standard and fair comparisons among models developed for disease outbreaks and outbreak data. \pkg{EpiCompare}'s major unique contribution to the existing approaches is a set of time-invariant tools (motivated in more detail in Section \ref{sec:time-invariant}). More broadly, \pkg{EpiCompare} aids the data analysis pipeline for infectious diseases by
\begin{enumerate}
  \item Standardizing outputs from common \proglang{R}-based infectious disease model software and common data storage types
  \item Expanding upon existing data visualization and EDA tools (especially in 3 state models like SIR models).
  \item Providing a interface for simple ODE-style agent based modeling.
  \item Aiding in comparison and assessment of models through time invariant analysis and conformal prediction bands and comparisons.
\end{enumerate}
Although \pkg{EpiCompare} aids in every part of the pipeline, our tools especially emphasize improvements for pipeline parts (1) and (4) which can be summarized as data input and output harmonization and contributions to fairly comparing models and data to one another.
